---
title: "Lab 8- Linear Regression in R"
author: "KL"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
salmon<-read_csv("salmon_imports.csv")
```
#Exploratory scatterplot
```{r}
salmon_scatter<- ggplot(salmon, aes(x = year, y= salmon_imports))+
  geom_point()
salmon_scatter

#Yes it looks like it makes sense to use a linear regression.
```

```{r}
salmon_model<- lm(salmon_imports ~ year, data = salmon)
salmon_model

#equation would be imports(tons) = -14982940 + 7550(Year)

```
The slope in this equation means that for every 1 year increase there is a 7550 increase in salmon pound imports.

The y - intercept in this equation means that at year 0, there was -14982940 salmon imports. This is concerning because we dont know when year 0 was and even if we did, there cannot be less than 0 salmon imports...This means that one needs to be careful when extrapolating this model for past values.

```{r}
par(mfrow = c(2,2))
plot(salmon_model)
#Residuals appear normally distributed other then a few outliers. There does not appear to be heteroscedasticity. 
summary(salmon_model)

```

Year significantly predicts salmon imports.
95% of variance in salmon imports is predictable from year.
5%??????

```{r}
salmon_final_graph<- ggplot(salmon, aes(x = year, y= salmon_imports))+
  geom_point()+
  geom_smooth(method = lm, se = TRUE, size = 0.5, color = "gray20") +
  theme_bw()+
  scale_x_continuous(expand = c(0,0), limits = c(1990, 2017))
  
salmon_final_graph
```

```{r}
new_years<- data.frame(year = c(2022, 2024, 2026, 2028))
future_predict<- predict(salmon_model, newdata = new_years, interval = "confidence")
future_predict

predictions<- data.frame(new_years, future_predict)
predictions
```

```{r}
test_name<- cor.test(salmon$year, salmon$salmon_imports)
test_name
#Pearson's r value is 0.9735387. This is very close to 1 so I would describe this as a strong positive correlation.
```












